---
title: "Visa Approval Rate"
author: "Otho Mantegazza"
date: today
format:
  html:
    toc: true
    # code-fold: true
    df-print: paged
execute: 
  warning: false
  echo: false
  error: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| message: false
library(tidyverse)
library(readxl)
library(janitor)
library(quantreg)
library(countrycode)
library(ggiraph)
library(broom)
library(glue)
library(ggrepel)

theme_set(
  theme_minimal()
)

css_default_hover <-
  girafe_css_bicolor(primary = "yellow",
                     secondary = "red")

cb_palette <- 
  c(Africa = '#228833',
    Americas = '#CCBB44',
    Asia = '#4477AA',
    Europe = '#EE6677',
    Oceania = '#AA3377')

highlight_countries <- c(
  'DZA',
  'NGA',
  'GHA',
  'SEN',
  'MAR',
  'ZAF'
  )
```

# Data

This analysis contains data from multiple sources:

1. World Bank GDP per capita, in current international dollars, downloaded manually from the [World Bank's website](https://datacatalog.worldbank.org/search/dataset/0037712/World-Development-Indicators).

    Indicator name: `GDP per capita, PPP (current international $)`.

```{r}
# Load development indicators ---------------------------------------------

dev_i <-
  # read_csv('data/WDIData.csv') %>% 
  read_csv('data/WDICSV.csv') %>% 
  clean_names() 
  
# Extract GDP and clean country names -------------------------------------

gdp_c <- 
  dev_i %>% 
  filter(
    # indicator_name == 'GDP per capita, PPP (current international $)'
    indicator_name == 'GNI per capita, Atlas method (current US$)'
  ) %>% 
  select(
    country_name,
    country_code,
    indicator_name, 
    indicator_code, 
    GDP_per_capita_eq_2019 = x2019,
    GDP_per_capita_eq_2021 = x2021,
    GDP_per_capita_eq_2022 = x2022,
  ) %>% 
  pivot_longer(
    cols = c(
      GDP_per_capita_eq_2019,
      GDP_per_capita_eq_2021,
      GDP_per_capita_eq_2022
    ),
    names_to = 'year',
    values_to = 'gdp_per_capita'
    ) %>% 
  mutate(year = year %>%
           str_remove('GDP_per_capita_eq_') %>%
           as.numeric())

	

```

2. Schengen short-stay visa statistics, downloaded manually from the [European Commission's Website](https://home-affairs.ec.europa.eu/policies/schengen-borders-and-visa/visa-policy_en#paragraph_1903).

    "A short-stay visa issued by one of the Schengen States entitles its holder to travel throughout the 27 Schengen States for up to 90 days in any 180-day period. Visas for visits exceeding that period remain subject to national procedures."
    
    The EU maintains a [list of country (PDF)](https://home-affairs.ec.europa.eu/system/files/2022-05/list%20of%20countries%20whose%20citizens%20must%20have%20a%20visa%20when%20crossing%20the%20external%20borders%20and%20those%20whose%20nationals%20are%20exempt%20from%20that%20requirement_en.pdf) that require visa to enter the Schengen area


```{r}
# Load visa stats ---------------------------------------------------------

read_and_clean_visa_stats <- function(path) {
  visa <-
    read_excel(path, 
               sheet = 2) %>% 
    clean_names() %>%  
    select(
      schengen_state,
      consulate_country = country_where_consulate_is_located,
      consulate_city = consulate,
      issued = total_at_vs_and_uniform_visas_issued_including_multiple_at_vs_me_vs_and_lt_vs,
      not_issued = total_at_vs_and_uniform_visas_not_issued
    ) %>% 
    drop_na(schengen_state) %>%
    mutate(
      across(
        .cols = c('schengen_state', 'consulate_country'),
        .fns = ~str_to_upper(.)
      )
    ) %>% 
    mutate(
      consulate_country = consulate_country %>% 
        recode('TÜRKIYE' = 'TURKEY')
    ) %>% 
    mutate(
      across(
        .cols = c('schengen_state', 'consulate_country'),
        .fns = ~countrycode(.,
                           origin = 'country.name',
                           destination = 'iso3c'),
        .names = '{.col}_code'
      )
    )
  
  return(visa)
}

visa_2023 <- 
  read_and_clean_visa_stats(
    'data/2023-schengen-visa-statistics-consulates_en.xlsx.xlsx'
  )

visa_2022 <- 
  read_and_clean_visa_stats(
    'data/Visa statistics for consulates in 2022_en.xlsx'
  )

visa_2019 <- 
  read_and_clean_visa_stats(
    'data/2019-consulates-schengen-visa-stats.xlsx'
  )
```

```{r}
exempt <-
  read_csv('data/short-stay-visa-exempt.csv') %>% 
  mutate(country_code = country_name %>% 
           countrycode(
             origin = 'country.name',
             destination = 'iso3c'
           )
  )

schengen_states <- 
  visa_2022 %>% 
  select(schengen_state,
         schengen_state_code) %>% 
  distinct() %>% 
  rename(country_name = schengen_state,
         country_code = schengen_state_code)

eu_27 <- 
  read_csv('data/eu-eurostat-codes.csv') %>% 
  mutate(country_code = country %>% 
           countrycode(
             origin = 'country.name',
             destination = 'iso3c'
           )
  ) %>% 
  select(
    country_name = country,
    country_code
  )

exempt_full <- 
  bind_rows(
    exempt,
    schengen_states,
    eu_27
  ) %>% 
  distinct(country_code) %>% 
  mutate(country_name = country_code %>% 
           countrycode(
             origin = 'iso3c',
             destination = 'country.name'
           )) %>% 
  arrange(country_name)
```


# Hypothesis

People from lower income countries face higher rejection rate when applying for a Schengen Visa.

Broad question: are we missing chances and possibilities, when we restrict travelling? Expecially when we restrict it inequally.

# Assumption

Visa request originating from one country, come from people with an income and purchasing power represented by that country's (Worldk Bank Indicators) statistics.

# Results

## All States

```{r}
model_country_level <- function(visa_stats, 
                                gdp_c) {
  
  country_level <- 
    visa_stats %>% 
    group_by(consulate_country, consulate_country_code) %>% 
    summarise(
      across(
        .cols = c('issued', 'not_issued'),
        .fns = ~sum(., na.rm = T)
      )
    ) %>% 
    ungroup() %>% 
    mutate(tot_request = issued + not_issued,
           ratio_rejected = not_issued/(tot_request)) %>% 
    left_join(gdp_c,
              by = c('consulate_country_code' = 'country_code')) 
  
  visa_binomial <- 
    country_level %>% 
    select(
      consulate_country,
      consulate_country_code,
      gdp_per_capita,
      issued,
      not_issued,
    ) %>% 
    drop_na(gdp_per_capita) %>% 
    group_by(consulate_country, gdp_per_capita) %>% 
    pivot_longer(cols = c(issued, not_issued),
                 names_to = 'outcome') %>% 
    ungroup() %>% 
    mutate(outcome_num = case_when(outcome == 'not_issued' ~ 1,
                                   outcome == 'issued' ~ 0))
  
  fit <- 
    glm(
      formula = outcome_num ~ gdp_per_capita,
      data = visa_binomial,
      weights = value, 
      family = 'binomial'
    )
  
  country_level <- 
    augment(
      fit,
      newdata = country_level,
      type.predict = "response"
    ) %>% 
    mutate(
      consulate_country_continent = 
        consulate_country_code %>% 
        countrycode(origin = 'iso3c',
                    destination = 'continent')
    )
  
  return(country_level)
}

country_level_2023 <-
  model_country_level(
    visa_2023,
    gdp_c %>% filter(year == 2022))

country_level_2022 <-
  model_country_level(
    visa_2022,
    gdp_c %>% filter(year == 2021))

country_level_2019 <-
  model_country_level(
    visa_2019,
    gdp_c %>% filter(year == 2019))

max_request <- 
  c(country_level_2019$tot_request,
    country_level_2022$tot_request) %>% 
  max(na.rm = T)

max_rejections <- 
  c(country_level_2019$ratio_rejected,
    country_level_2022$ratio_rejected) %>% 
  max(na.rm = T)

max_gdp_pc <- 
  gdp_c$gdp_per_capita %>% 
  max(na.rm = T)
```

```{r}
plot_model <- function(modelled_data,
                       year,
                       gdp_year,
                       title =  glue("Schengen Visa Rejection Rate in {year}"),
                       model = TRUE,
                       width = 200,
                       ratio = 4/3) {
  country_level_scatter <- 
    modelled_data %>% 
    # drop_na(GDP_per_capita_eq_2021, ratio_rejected) %>% 
    ggplot() +
    aes(x = gdp_per_capita,
        colour = consulate_country_continent,
                        y = ratio_rejected) +
    {if(model)geom_line(aes(y = .fitted),
                        colour = 'grey30',
                        lty = '31',
                        size = 0.8)} +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_point_interactive(aes(size = tot_request,
                               tooltip = consulate_country,
                               data_id = consulate_country_code),
                           alpha = .9,
                           hover_nearest = TRUE) +
    labs(x = glue('GDP per Capita from previous year in equivalent dollars ($)'),
         y = 'Percent of Applications Rejected',
         size = 'Applications Received',
         colour = 'Continent',
         title = title,
         subtitle = "(By country in which the visa application was lodged)") +
    scale_size_continuous(range = c(0, 15),
                          breaks = c(1e3, 1e4, 1e5, 1e6),
                          limits = c(0, max_request)) +
    scale_y_continuous(labels = scales::percent,
                       limits = c(0, max_rejections)) +
    scale_x_continuous(limits = c(0, max_gdp_pc)) + 
    scale_colour_manual(values = cb_palette)
  
  
  ggsave(filename = glue('output/{title}-labels-PAKISTAN-WIDE.jpg'), 
         plot = country_level_scatter +
           geom_text_repel(
             data = . %>% filter(
               consulate_country_code %in% highlight_countries
             ),
             mapping = aes(label = consulate_country),
             colour = 'black',
             min.segment.length = 0, 
             # nudge_x = 2e4,
             # nudge_y = .1, 
             xlim = c(3e4, NA),
             ylim = c(0.25, NA),
             size = 3,
             direction = 'y',
             force = .1, 
             segment.size = 0.2,
           ),
           # theme(legend.position = "bottom",
           #       legend.box="vertical"),
         width = width,
         height = width/ratio,
         units = 'mm') 
  
  ggsave(filename = glue('output/{title}-WIDE.jpg'),
         plot = country_level_scatter,
           # theme(legend.position = "bottom",
           #       legend.box="vertical"),
         width = width,
         height = width/ratio,
         units = 'mm')
  
  x <- girafe(ggobj = country_level_scatter
                # theme(legend.position = "bottom"
                #  legend.box="vertical")
              )
  x <- girafe_options(x, opts_hover(css = "stroke:red;stroke-width:3px"))

  
  return(x)
}
```


```{r}
#| column: screen-inset-right
#| fig-width: 8
plot_model(country_level_2022, year = 2022, gdp_year = 2021)

```


```{r}
#| column: screen-inset-right
#| fig-width: 10
plot_model(country_level_2019, 2019, gdp_year = 2019)
```

## Removing Exempt Countries

In 2022, passport holders of `r nrow(exempt)` countries are exempt from Schengen short-stay visa when crossing the borders. These countries are [documented here (PDF)](https://home-affairs.ec.europa.eu/system/files/2022-05/list%20of%20countries%20whose%20citizens%20must%20have%20a%20visa%20when%20crossing%20the%20external%20borders%20and%20those%20whose%20nationals%20are%20exempt%20from%20that%20requirement_en.pdf). Obviously, also `r nrow(exempt_full) - nrow(exempt)` Schengen and EU States are exempt.

Visa request from those countries probably comes from migrant population.

::: {.callout-caution}
I'm not sure how to deal with Cyprus, Romania and Bulgaria, which are in a strange situation regarding Schengen and EU.
:::

```{r}
#| tbl-cap: "Exempt countries:"
exempt_full
```

```{r}
country_level_2022_not_exempt <-
  model_country_level(
    visa_2022 %>% filter( ! consulate_country_code %in% exempt_full$country_code),
    gdp_c %>% filter(year == 2021))
```


```{r}
#| column: screen-inset-right
#| fig-width: 10
plot_model(country_level_2022_not_exempt,
           year = 2022,
           gdp_year = 2021,
           title = "Schengen Visa Rejection Rate in 2022 - Not Exempt States")
```

```{r}
country_level_2022_exempt <-
  model_country_level(
    visa_2022 %>% filter(consulate_country_code %in% exempt_full$country_code),
    gdp_c %>% filter(year == 2021))
```


```{r}
#| column: screen-inset-right
#| fig-width: 10
plot_model(country_level_2022_exempt,
           year = 2022,
           gdp_year = 2021,
           title = "Schengen Visa Rejection Rate in 2022 - Exempt States",
           model = FALSE)
```

```{r}
#| column: screen-inset-right
#| fig-width: 10

set.seed(1);plot_model(
  country_level_2023,
  year = 2023,
  gdp_year = 2022,
  title = "Schengen Visa Rejection Rate in 2023"
)
```

```{r}
# save(country_level_2023, "data/count")
```


```{r}
#| eval: false
# Plot binomial stratified by country -------------------------------------

# visa_by_gdp_consulate_schstate <-  
#   visa %>% 
#   group_by(schengen_state, consulate_country) %>% 
#   summarise(
#     across(
#       .cols = c('issued', 'not_issued'),
#       .fns = ~sum(., na.rm = T)
#     )
#   ) %>% 
#   ungroup() %>% 
#   mutate(tot_request = issued + not_issued,
#          ratio_rejected = not_issued/(tot_request)) %>% 
#   left_join(gdp_c,
#             by = c('consulate_country' = 'country_name'),
#             keep = T) %>% 
#   # mutate(consulate_country = consulate_country %>%
#   #          factor(levels = countries_by_gdp_c)) %>% 
#   select(schengen_state,
#          consulate_country,
#          GDP_per_capita_eq_2021,
#          issued,
#          not_issued,
#          tot_request,
#          ratio_rejected) %>% 
#   drop_na(consulate_country)
# 
# visa_for_by_consulate_binomial <- 
#   visa_by_gdp_consulate_schstate %>% 
#   select(
#     schengen_state,
#     consulate_country,
#     GDP_per_capita_eq_2021,
#     issued,
#     not_issued,
#   ) %>% 
#   group_by(schengen_state, consulate_country, GDP_per_capita_eq_2021) %>% 
#   pivot_longer(cols = c(issued, not_issued),
#                names_to = 'outcome') %>% 
#   ungroup() %>% 
#   mutate(outcome_num = case_when(outcome == 'not_issued' ~ 1,
#                                  outcome == 'issued' ~ 0))
# 
# 
# visa_by_gdp_consulate_schstate %>% 
#   ggplot() +
#   aes(x = GDP_per_capita_eq_2021) +
#   geom_point(aes(size = tot_request,
#                  y = ratio_rejected),
#              alpha = .7) +
#   geom_smooth(data = visa_for_by_consulate_binomial,
#               aes(weight = value,
#                   y = outcome_num),
#               method = 'glm',
#               method.args = list(family = "binomial"),
#               colour = '#8800FF') +
#   geom_hline(yintercept = 0) +
#   geom_vline(xintercept = 0) +
#   facet_wrap(facets = "schengen_state") +
#   labs(x = 'GDP per Capita in 2021 Equivalent Dollars',
#        y = 'Percent of Application Rejected',
#        size = 'Applications received',
#        title = "Schengen Visa Rejection Rate",
#        subtitle = "(by country in which the visa application was lodged)") +
#   lims(y = c(0, NA)) +
#   scale_size_continuous(range = c(0, 5),
#                         breaks = c(1e3, 1e4, 1e5)) +
#   scale_y_continuous(labels = scales::percent)
# 
# # extra ???? --------------------------------------------------------------
# 
# countries_by_gdp_c <- 
#   gdp_c %>% 
#   filter(country_name %in% visa$consulate_country) %>% 
#   arrange(GDP_per_capita_eq_2021) %>% 
#   drop_na() %>% 
#   pull(country_name)
# 
# 
# visa_gdp_consulate <- 
#   visa_by_gdp %>% 
#   mutate(consulate_country = consulate_country %>% factor(levels = countries_by_gdp_c)) %>% 
#   select(consulate_country, tot_request, ratio_rejected) %>% 
#   drop_na(consulate_country)
# 

# visa_gdp_consulate %>% 
#   ggplot() +
#   aes(x = ratio_rejected,
#       y = consulate_country,
#       fill = tot_request) +
#   geom_col()

# geom_point(aes(size = tot_request),
#            alpha = .7) +
# geom_smooth(aes(weight = tot_request),
#             method = 'lm',
#             formula = 'y ~ poly(x, 3)', 
#             se = FALSE) +
# stat_boxplot(aes(group = cut_interval(GDP_per_capita_eq_2021, 10),
#                  weight = tot_request),
#              # geom = 'point',
#              fill = '#00000044',
#              outlier.alpha = 0) +
```