---
title: "Short Term Visa Accessibility"
editor_options: 
  chunk_output_type: console
execute: 
  warning: false
---
<!--- js dependencies -->
<script src="https://d3js.org/d3.v7.min.js"></script>
<script src="js/scatterplot.js"></script>

```{r}
#| include: false
oldwd <- getwd()
#setwd('~/Desktop/visa-lago/')
source(knitr::purl('explore.qmd'))
#setwd(oldwd)
country_level_2022 %>% 
  select(
    consulate_country,
    consulate_country_code,
    consulate_country_continent,
    tot_request,
    gdp_per_capita,
    ratio_rejected,
    fitted = .fitted
  ) %>% 
  write_csv('data/2022-country-level-clean.csv')

country_level_2023 %>% 
  # select(
  #   consulate_country,
  #   consulate_country_code,
  #   consulate_country_continent,
  #   tot_request,
  #   gdp_per_capita,
  #   ratio_rejected,
  #   fitted = .fitted
  # ) %>% 
  write_csv('data/2023-country-level-clean.csv')
```

```{r}
ojs_define(
  country_level_2022 = country_level_2022 %>% 
    select(
      consulate_country,
      consulate_country_code,
      consulate_country_continent,
      tot_request,
      gdp_per_capita,
      ratio_rejected,
      fitted = .fitted
    ) %>% 
    drop_na() %>% 
    {
    transpose(.l = .)
  }
)

ojs_define(
  country_level_2023 = country_level_2023 %>% 
    select(
      consulate_country,
      consulate_country_code,
      consulate_country_continent,
      tot_request,
      gdp_per_capita,
      ratio_rejected,
      fitted = .fitted
    ) %>% 
    drop_na() %>% 
    {
    transpose(.l = .)
  }
)
```

```{ojs}
height = 500
cb_palette = {
  let cb_palette = {
  Africa: "#228833",
  Americas: "#CCBB44",
  Asia: "#4477AA",
  Europe: "#EE6677",
  Oceania: "#AA3377",
  }
  return cb_palette
}
```

## Schengen Visa Rejection Rate

(By country in which the visa application was lodged)

### Year 2022

```{ojs} 
Scatterplot(country_level_2022,
  {
    x: d => d.gdp_per_capita,
    y: d => d.ratio_rejected,
    area: d => d.tot_request,
    fill: d => d.consulate_country_continent,
    id: d => d.consulate_country_code,
    label: d => d.consulate_country,
    fitted: d => d.fitted,
    fillPalette: cb_palette,
    width: width,
    height: height,
    voronoiShow: false,
    year: 2022,
  }
)
```

### Year 2023

```{ojs} 
Scatterplot(country_level_2023,
  {
    x: d => d.gdp_per_capita,
    y: d => d.ratio_rejected,
    area: d => d.tot_request,
    fill: d => d.consulate_country_continent,
    id: d => d.consulate_country_code,
    label: d => d.consulate_country,
    fitted: d => d.fitted,
    fillPalette: cb_palette,
    width: width,
    height: height,
    voronoiShow: false,
    year: 2023
  }
)
```

:::: {.grid}

::: {.g-col-12 .g-col-md-6}

### Data Sources

Data on short-term visa applications and rejection rate are released publicly by the Directorate-General for Migration and Home Affairs of the European Commission, and are [available on their website](https://home-affairs.ec.europa.eu/policies/schengen-borders-and-visa/visa-policy_en#paragraph_1903).

Data on GDP per capita are estimated and made available by the World Bank, [on their website](https://datacatalog.worldbank.org/search/dataset/0037712/World-Development-Indicators). We have used the “GDP per capita, at purchasing power parity (current international $)” indicator as a basic measurement indicating average wealth per nation.
Data Analysis

:::

::: {.g-col-12 .g-col-md-6}

### Data Analysis

We have used ISO3166 alpha-3-codes to merge the data in the two datasets, relying on the R package [countrycode](https://joss.theoj.org/papers/10.21105/joss.00848) to convert country names into country codes when needed.

The regression line uses a [binomial generalised linear model](https://stat.ethz.ch/R-manual/R-devel/library/stats/html/00Index.html) to estimate conservatively how much we can expect the application rejection rate to increase when the GDP per capita of the originating country decreases. 

African countries are often outliers, with rejection rates well above what is expected by the regression line.

:::

::::

## UK Visitor Visa Rejection Rate by Nationality

```{r}
library(tidyverse)
library(janitor)
library(countrycode)
library(grid)

theme_set(theme_minimal(base_size = 16))

cb_palette <- 
  c(Africa = '#339944',
    Americas = '#DDCC55',
    Asia = '#5588BB',
    Europe = '#EE6677',
    Oceania = '#AA3377')
```

```{r}
visa_uk_mar <- 
  read_tsv('data/UK-visas-summary-mar-2023-tables.tsv')

visa_uk_dec <- 
  read_tsv('data/UK-visas-summary-dec-2023-tables.tsv')
```

```{r}
custom_currency_scale <- 
  scales::label_currency(
    prefix = "£ ",
    accuracy = 1,
    scale_cut = c(k=1e3)#scales::cut_short_scale()
  )

plot_uk_visa <- function(visa_uk, 
                         year_ending = "March 2023",
                         show_cost = TRUE) {

 visa_uk <- 
  visa_uk %>% 
  mutate(grant_rate = grant_rate %>% str_remove('%') %>% as.numeric()) %>% 
  mutate(grant_rate = grant_rate/100,
         rej_rate = 1-grant_rate) %>% 
  mutate(continent = countrycode(nationality,
                                 origin = 'country.name',
                                 destination = 'continent'))

  p <-
    visa_uk %>% 
    arrange(desc(rej_rate)) %>% 
    mutate(nationality = nationality %>% as_factor()) %>% 
    ggplot() +
    aes(y = nationality,
        x = rej_rate) +
    geom_segment(aes(yend = after_stat(y),
                     xend = 0),
                 linewidth = .5,
                 lty = '11') +
    geom_point(aes(size = resolved,
                   fill = continent),
               alpha = 1,
               pch = 21) +
    geom_vline(xintercept = 0,
               linewidth = 1.5) +
    labs(x = "Visa Rejection Rate",
         y = "Nationality",
         size = "Size:\nApplications Received",
         fill = "Colour:\nContinent",
         title = "UK Visitor Visa Rejection Rate by Nationality",
         subtitle = glue::glue("Year Ending {year_ending}")) +
    guides(fill = guide_legend(override.aes = list(size = 5)),
           size = guide_legend(override.aes = list(shape = 21,
                                                   fill = "white"))) +
    scale_x_continuous(limits = c(0, 1.05),
                       labels = scales::percent,
                       expand = expansion(0, 0),
                       breaks = c(0, .2, .4, .6, .8, 1)) +
    scale_size_continuous(range = c(0, 15),
                          labels = scales::comma) +
    scale_fill_manual(values = cb_palette) +
    theme(panel.grid.major.y = element_blank(),
          panel.grid.minor = element_blank(),
          panel.grid.major.x = element_line(colour = 'black',
                                            size = .1),
          # axis.title = element_text(hjust = 1),
          legend.justification = "top")

  if(show_cost) {
    p <-
      p +
      geom_text(
        data = . %>%
        filter(
          nationality %in% c(
            "Nigeria",
            "Pakistan",
            "Algeria",
            "Bangladesh",
            "Ghana",
            "Morocco"
          )
        ),
        aes(
          x = rej_rate,
          label = paste(
                  refusal %>% `*`(100) %>% map_chr(custom_currency_scale)
              ),
          hjust = -.2 - (resolved/max(resolved))/4
        )
      ) +
      annotate(
        label = "↓ Cost of rejections in thousands of British pounds",
        geom = "text",
        x = .07,
        y = 21.2,
        vjust = 1,
        hjust = 0
      )
  }
  
  # ggsave(plot = p,
  #        filename = 'output/uk-visa.jpg',
  #        width = 10, height = 10)
  
  p <- ggplotGrob(p)
  
  # png(filename = 'output/uk-visa-2023-q1.png',
  #     width = 25,
  #     height = 25,
  #     units = "cm",
  #     res = 300)
  grid.newpage()
  grid.draw(p)
  grid.text(x = 0.76,
            y = 0.4,
            gp = gpar(fontsize = 12),
            label = str_wrap(
              glue::glue("Visitor visa applications and outcomes, by nationality, in the year ending {year_ending}. Top 20 nationalities applying for visitor visas in the year. Data relates to entry clearance visa applications made outside the UK. Includes main applicants and dependants."),
              width = 28),
            hjust = 0,
            vjust = 1)
  grid.text(x = 0.76,
            y = 0.10,
            gp = gpar(fontsize = 8),
            label = str_wrap(
              "Data from www.gov.uk",
              width = 28),
            hjust = 0,
            vjust = 1)
  # dev.off()
}
```

### Year Ending March 2023

```{r}
#| fig-width: 10
#| fig-height: 9
plot_uk_visa(visa_uk_mar, year_ending = "March 2023",
             show_cost = F)
```

### Year Ending December 2023

```{r}
#| fig-width: 10
#| fig-height: 9
plot_uk_visa(visa_uk_dec, year_ending = "December 2023",
             show_cost = F)
```

```{r}
#| message: false
# svglite::svglite("output/uk-year-ending-dec-2023.svg")
# plot_uk_visa(visa_uk_dec, year_ending = "December 2023")
# dev.off()
```

## Access to the Data

The dataset utilised for the analysis of short-term visa regimes is available [here](https://docs.google.com/spreadsheets/d/1Cy6cpS03LtGuitxJVjffzyTMEdkRrECj/). It includes rejection rates and the associated costs of rejections for both Schengen and UK visa applications. When referencing this analysis, please acknowledge Marta Foresti - Founder, LAGO Collective & Visiting Senior Fellow, ODI and Otho Mantegazza - Research Scientist, Data Analyst.

The original data is sourced from:

- [Directorate-General for Migration and Home Affairs of the European Commission](https://home-affairs.ec.europa.eu/policies/schengen-borders-and-visa/visa-policy/short-stay-visas-issued-schengen-countries_en) (Schengen)
- [UK Home Office](https://www.gov.uk/government/statistical-data-sets/immigration-system-statistics-data-tables#entry-clearance-visas-granted-outside-the-uk) (UK)
